---
title: "Site XXX - [NAME] VOC Data"
author: "Will Clagett"
date: "YYYY-MM-DD"
output: html_document
---
```{r packages, include=FALSE}
library(readr)
library(knitr)
library(dplyr)
library(plyr)
library(forcats)
library(ggplot2)
library(tidyr)
library(purrr)
library(faraway)
library(cowplot)
library(reshape2)
library(corrplot)
library(tibble)
library(scales)
library(ggthemes)
library(stringr)
library(gridExtra)
library(patchwork)
library(gghighlight)
library(ggdark)
library(viridis)
library(DT)
library(plotly)
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# **VOC Data**
## **Site XXX - NAME**
## **dd Mmm - dd Mmm YYYY**
## *[CITY], CO*
```{r, site_photo, out.width="50%"}
include_graphics("./graphics/[file name].jpg")
```


---

## data set
[add the location description here]
Summa Canisters were deployed in ___ locations at the site:

 - X outdoor
 - X inside facility

| Rooms sampled in facility |
|:------|
| 1.  |
| 2.  |
| 3.  |
| 4.  |
| 5.  |

---

```{r load_data, include=FALSE}
#load data
#FIND AND REPLACE SITE_ID in csv file, double check rows to slice, col. to select
site_XXX <- (read_csv(file = "./data/site_XXX_summa_data.csv")) %>% 
  slice(2:5, 7:8) %>%
  select(1,7:67)

#pivot data for plots
p.analytes <- site_XXX %>% 
  pivot_longer(- ID,
               names_to = "analyte",
               values_to = "conc.")
#VOC classes as objects
alc <- c("isopropanol", "butanol")
ald <- c("acetaldehyde")
aro <- c("cyclopentane", "cyclohexane", "methylcyclohexane")
btx <- c("benzene", "toluene", "ethylbenzene", "m+p-xylene", "o-xylene",
          "isopropylbenzene", "n-propylbenzene", "3-ethyltoluene",
          "4-ethyltoluene", "1,3,5-trimethylbenzene", "2-ethyltoluene",
          "1,2,4-trimethylbenzene", "1,2,3-trimethylbenzene",
          "1,3-diethylbenzene", "1,4-diethylbenzene")
chl <- c("C2HCl3", "C2Cl4")
kt <- c("acetone")
oth <- c("isoprene", "styrene", "acetonitrile", "methylethylketone",
           "a-pinene", "b-pinene", "limonene", "camphene", "methane")
stc <- c("ethane", "propane", "i-butane", "n-butane", "i-pentane",
                    "n-pentane", "n-hexane", "2,4 dimethylpentane", "n-heptane",
                    "2,3-dimethylpentane", "2-methylhexane", "3-methylhexane",
                    "2,2,4-trimethylpentane", "2,3,4-trimethylpentane",
                    "2-methylheptane", "3-methylheptane", "n-octane", "n-nonane",
                    "n-decane", "ethene", "propene", "t-2-butene", "1-butene",
                    "c-2-butene", "t-2-pentene", "1-pentene", "cis-2-pentene",
                    "ethyne")
#add voc categories to dfs
voc <- p.analytes %>% 
  mutate(category = case_when(p.analytes$analyte %in% alc ~ "Alc.",
                              p.analytes$analyte %in% ald ~ "Ald.",
                              p.analytes$analyte %in% stc ~ "Stc.",
                              p.analytes$analyte %in% aro ~ "Aro.",
                              p.analytes$analyte %in% btx ~ "Btx.",
                              p.analytes$analyte %in% chl ~ "Chl.",
                              p.analytes$analyte %in% kt ~ "Ktn.",
                              p.analytes$analyte %in% oth ~ "Oth."))

#create outdoor group
outdoor <- voc %>% 
  filter(ID =="outdoor")
#change conc. to numeric
voc$conc. <- as.numeric(as.character(voc$conc.))
outdoor$conc. <- as.numeric(as.character(outdoor$conc.))
#calculate ratios
voc <- voc %>%
  group_by(ID, analyte) %>%
  ungroup() %>% 
  mutate(od_ratio = round(as.numeric(voc$conc.)/as.numeric(outdoor$conc.), 2))
#highlight methane
methane <- voc %>% 
  filter(analyte == "methane")

#UPDATE LOCATIONS FOR THE SITE YOU ARE CURRENTLY WORKING ON Location 1, 2, etc.!
#default is alphabetical order
#subgroups,
#all indoor locations
indoor <- voc %>% 
  filter(ID != "outdoor")
#location1
location1 <- voc %>% 
  filter(ID == "[location1]")
#location2
location2 <- voc %>% 
  filter(ID == "[location2]")
#location3
location3 <- voc %>% 
  filter(ID == "[location3]")
#location4
location4 <- voc %>% 
  filter(ID == "[location4]")
#location5
location5 <- voc %>% 
  filter(ID == "[location5]")
#location6
location6 <- voc %>% 
  filter(ID == "[location6]")

#for DT and plotlys
voc2 <- p.analytes %>% 
  mutate(category = case_when(p.analytes$analyte %in% alc ~ "Alcohol",
                              p.analytes$analyte %in% ald ~ "Aldehyde",
                              p.analytes$analyte %in% stc ~ "Straight Chain",
                              p.analytes$analyte %in% aro ~ "Aromatic",
                              p.analytes$analyte %in% btx ~ "Btex",
                              p.analytes$analyte %in% chl ~ "Chlorinated",
                              p.analytes$analyte %in% kt ~ "Ketone",
                              p.analytes$analyte %in% oth ~ "Other"))

voc2$conc. <- as.numeric(as.character(voc$conc.))
voc2 <- voc2 %>%
  group_by(ID, analyte) %>%
  ungroup() %>% 
  mutate(od_ratio = round(as.numeric(voc2$conc.)/as.numeric(outdoor$conc.), 2))
indoor2 <- voc2 %>% 
  filter(ID != "outdoor")

```


## Data Table
```{r data_table}
datatable(voc2, colnames = c("Location", "Analyte", "Concentration",
                               "Category", "Outdoor Ratio"),
          options = list(pageLength = 10), rownames = FALSE)

```

---

## Summary Plots of all VOCs

Plot of all VOC in All Locations
```{r plot_all, out.width = "150%", warning=FALSE, message=FALSE}

voc_plot <- ggplot(voc, aes(x = reorder(analyte, conc.),
                            y = conc., color = ID)) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc.)) +
  # guides(size = "none") +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  theme_calc() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  xlab("Analytes") +
  ylab("Concentration\n(VOC ppbv or methane ppmv)") +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")
voc_plot +
  scale_color_manual(values = c("#261e1b","#af6f70","#fbc117","#color",
                                "#color", "#color", "#color"),
                     labels = c("location1", "location2", "location3",
                                "outdoor", "location4",
                                "location5", "location6"))

```


Plot of all VOC in All Locations using plotly
```{r plotly_all_VOCs, fig.align = "center", fig.dim=c(15,10), warning=FALSE, message=FALSE}
#plot all VOCs at site
voc_plotly <- ggplot(voc2, aes(x = reorder(analyte, conc.),
                            y = conc., color = ID,
                            text = paste("Analyte: ", analyte,
                                         "<br> Conc. :", conc.,
                                         "<br> Class: ", category))) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc.)) +
  # guides(size = "none") +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  theme_calc() + #try using different themes here
  theme(axis.text.x = element_text(size = 9, angle = 45, hjust = 1)) +
  scale_colour_tableau() +
  xlab("Analytes") +
  ylab("Concentration\n(VOC ppbv or methane ppmv)") +
  ggtitle("Site XXX:[NAME] Summa Cannister Deployment")
ggplotly(voc_plotly, tooltip = "text")

```

Combo plot of all VOC in all locations dot, line
```{r dot_line_all, out.width = "150%", warning=FALSE, message=FALSE}

voc_combo_point <- ggplot(indoor, aes(color = ID, x = analyte, y = conc.)) +
  geom_point(data = indoor, aes(x = analyte, y = conc.),
             shape = 18, size = 3, alpha = 0.5) +
  geom_line(data = outdoor, aes(x = analyte, y =  conc.,
                                group = ID, alpha = 0.5)) +
  guides(alpha = "none") +
  xlab("Analytes") +
  ylab(expression(atop("Concentration",paste("(VOC ppbv or methane ppmv)")))) +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  dark_theme_bw() +
  theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
        legend.position = c(0.11,0.73)) +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")
voc_combo_point+
  scale_color_manual(values = c("#fde725", "#7ad151",
                                  "#22a884", "#2a788e", "#414487",
                                  "#440154"),
                       labels = c("location1", "location2",
                                "location3", "Outdoor",
                                "location4", "location5")) +
  theme(legend.title = element_text(color = "cyan", size = 10),
                 legend.text = element_text(color = "white"))

```

Plot of all VOC in All Locations Lava Theme
```{r plot_all_lava, out.width = "135%", warning=FALSE, message=FALSE}

gr_lava <- ggplot(voc, aes(x = reorder(analyte, conc.),
                y = conc., color = ID)) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc.)) +
  # guides(size = "none") +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  theme_bw() +
   theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
        legend.position = c(0.11,0.73)) +
  xlab("Analytes") +
  ylab("Concentration\n(VOC ppbv or methane ppmv)") +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")
gr_lava +
  scale_color_manual(values = c("#bc2e16", "#7a2a1c",
                                "#f64009", "#af6f70", "#e66d1d",
                                "#fbc117"),
                     labels = c("location1", "location2",
                                "location3", "Outdoor",
                                "location4", "location5")) +
  theme(legend.title = element_text(color = "#d1644b", size = 10),
        legend.text = element_text(color = "#261e1b"))
```


Facet wrap by location
```{r facet_location, out.width = "150%", warning=FALSE, message=FALSE}

loc_fctw <- ggplot(voc, aes(x = reorder(analyte, conc.),
                            y = conc.)) +
  geom_point(color = "#50C878", shape = 18, alpha = 0.5) +
  geom_point(data = methane, aes(x = analyte, y = conc.,
                                 color ="red")) +
  guides(size = "none", color = "none") +
  xlab("Analytes") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  facet_wrap(~ID, scales = "free_y") +
  theme(axis.text.x = element_text(size = 3, angle = 45, hjust = 1)) +
  labs(x = "Analytes", y = "Concentration") +
  ggtitle("Grouped by Cannister location")
#loc_fctw
```

```{r facet_location_plotly, fig.dim=c(13,10), warning=FALSE, message=FALSE}

loc_fctw_slr <- ggplot(voc, aes(x = reorder(analyte, conc.),
                            y = conc.,
                            text = paste("Analyte: ", analyte,
                                         "<br> Conc. :", conc.,
                                         "<br> Class: ", category))) +
  geom_point(color = "#50C878", shape = 18, alpha = 0.5) +
  geom_point(data = methane, aes(x = analyte, y = conc.,
                                 color ="red")) +
  guides(size = "none", color = "none") +
  xlab("Analytes") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  theme_solarized() +
  facet_wrap(~ID, scales = "free_y") +
  theme(axis.text.x = element_text(size = 3, angle = 45, hjust = 1)) +
  labs(x = "Analytes", y = "Concentration")

ggplotly(loc_fctw_slr, tooltip = "text")


```

All plot and facet wrap
```{r all_and_facet, out.width = "135%", warning=FALSE, message=FALSE}

voc_plot +
  loc_fctw +
  plot_layout(nrow = 2, heights = c(2, 2))

```

Facet grid by VOC category
```{r facet_grid_voc_cat, out.width = "175%", warning=FALSE, message=FALSE}

voc_fctg <- ggplot(voc, aes(x = reorder(analyte, conc.),
                            y = conc., color = ID)) +
  geom_point(shape = 18, alpha = 0.5) +
  geom_point(data = methane, aes(x = analyte, y = conc.)) +
  guides(size = "none") +
  facet_grid(~ category, scales = "free_x") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  facet_grid(.~ category, scales = "free", switch = "x", space = "free_x") +
  theme_bw() +
  theme(strip.placement = "outside", strip.text = element_text(size  = 8),
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  labs(x = "Analytes Grouped in VOC Categories",
       y = "Concentration\n(VOC ppbv or methane ppmv)") 

voc_fctg +
  scale_color_manual(values = c("#065143", "#839b5d",
                                "#df5e21", "#3f88c5", "#aab6cb",
                                "#bc2e16"),
                     labels = c("location1", "location2",
                                "location3", "Outdoor",
                                "location4", "location5")) +
  theme(legend.title = element_text(color = "black", size = 10),
        legend.text = element_text(color = "black"))
```

Facet grid indoor
```{r acet_grid_indoor, out.width = "190%", warning=FALSE, message=FALSE}

indoor_fctg <- ggplot(indoor, aes(color = ID, x = analyte, y = conc.)) +
  geom_point(data = indoor, aes(x = reorder(analyte, conc.), y = conc.),
             size = 3, shape = 18, alpha = 0.5) +
  facet_grid(.~ category, scales = "free", space = "free") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  labs(x = "Analytes Grouped in VOC Categories",
       y = "Concentration\n(VOC ppbv or methane ppmv)") +
  ggtitle("Grouped by Analyte Class")

indoor_fctg +
  scale_color_manual(values = c("#3090C7", "#FFE87C",
                                "#A74AC7", "#12AD2B", "#C04000",
                                "#F98B88"),
                     labels = c("location1", "location2",
                                "location3", "Outdoor",
                                "location4", "location5")) +
  theme(legend.title = element_text(color = "black", size = 10),
        legend.text = element_text(color = "black"))


```

## Top 5 Concentrations Plots by Location
```{r top_five_data, include=FALSE}
#outdoor
od_top <- outdoor %>% 
  group_by(analyte) %>% 
  arrange(desc(conc.))
od_top <- top_n(ungroup(od_top), 5, conc.) 
#location1
location1_top <- location1 %>% 
  group_by(analyte) %>% 
  arrange(desc(conc.))
location1_top <- top_n(ungroup(location1_top), 5, conc.) 
#location2
location2_top <- location2 %>% 
  group_by(analyte) %>% 
  arrange(desc(conc.))
location2_top <- top_n(ungroup(location2_top), 5, conc.)
#location3
location3_top <- location3 %>% 
  group_by(analyte) %>% 
  arrange(desc(conc.))
location3_top <- top_n(ungroup(location3_top), 5, conc.)
#location4
location4_top <- location4 %>% 
  group_by(analyte) %>% 
  arrange(desc(conc.))
location4_top <- top_n(ungroup(location4_top), 5, conc.)
#location5
location5_top <- location5 %>% 
  group_by(analyte) %>% 
  arrange(desc(conc.))
location5_top <-  top_n(ungroup(location5_top), 5, conc.)
#outdoor
outdoor_top <- outdoor %>% 
  group_by(analyte) %>% 
  arrange(desc(od_ratio))
outdoor_top <-  top_n(ungroup(outdoor_top), 5, od_ratio)


```


```{r location1_t, warning=FALSE, message=FALSE}
p_location1_top <- location1_top %>% 
  ggplot() +
  geom_bar(aes(x = reorder(analyte, conc.), y = conc.),
           stat = "identity", fill = "#065143") +
  labs(x = "location1", y = "Concentration") +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
               labels = trans_format("log10", math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))

p_location1_top + theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"))

```


```{r location2_t, warning=FALSE, message=FALSE}

p_location2_top <- location2_top %>% 
  ggplot() +
  geom_bar(aes(x = reorder(analyte, conc.), y = conc.),
           stat = "identity", fill = "#A74AC7") +
  labs(x = "location2", y = "Concentration") +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
               labels = trans_format("log10", math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))

p_location2_top + theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"))

```


```{r location3_t, warning=FALSE, message=FALSE}

p_location3_top <- location3_top %>% 
  ggplot() +
  geom_bar(aes(x = reorder(analyte, conc.), y = conc.),
           stat = "identity", fill = "#F98B88") +
  labs(x = "location3", y = "Concentration") +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
               labels = trans_format("log10", math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))

p_location3_top + theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"))

```


```{r location4_t, warning=FALSE, message=FALSE}

p_location4_top <- location4_top %>% 
  ggplot() +
  geom_bar(aes(x = reorder(analyte, conc.), y = conc.),
           stat = "identity", fill = "#C04000") +
  labs(x = "location4", y = "Concentration") +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
               labels = trans_format("log10", math_format(10^.x))) +
  theme_economist()
  # theme_bw() +
  # theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))

p_location4_top  
# + theme(
#   panel.background = element_rect(fill = "lightblue",
#                                 colour = "lightblue",
#                                 size = 0.5, linetype = "solid"))

```


```{r location5_t, warning=FALSE, message=FALSE}

p_location5_top <- location5_top %>% 
  ggplot() +
  geom_bar(aes(x = reorder(analyte, conc.), y = conc.),
           stat = "identity", fill = "tomato2") +
  labs(x = "location5", y = "Concentration") +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
               labels = trans_format("log10", math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))

p_location5_top + theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"))

```


```{r, warning=FALSE, message=FALSE}

grid.arrange(p_location1_top, p_location2_top, p_location3_top, p_location4_top, p_location5_top,
             ncol = 3, nrow = 2,
             top = "Top 5 Analytes in Each Location", left = "Outdoor Ratio")

```


## Indoor to Outdoor Ratio Plots
Outdoor Ratio all Locations
```{r outdoor_ratios}
# ratio_plot <- ggplot(indoor, aes(x = reorder(analyte, od_ratio),
#                               y = od_ratio, color = ID)) +
#   geom_point(shape = 18, size = 1, alpha = 0.5) +
#   # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
#   # guides(size = "none") +
#   scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
#                 labels = trans_format(`log10`, math_format(10^.x))) +
#   theme_bw() +
#   theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
#   xlab("Analytes") +
#   ylab("Indoor to Outdoor Ratios") +
#   ggtitle("Site XXX Summa Cannister Deployment",
#           "Mmm. dd - Mmm. dd, YYYY. City, CO")
# ratio_plot
```

```{r ratio_plot, out.width = "135%", warning=FALSE, message=FALSE}

ratio_plot <- ggplot(indoor, aes(x = reorder(analyte, od_ratio),
                              y = od_ratio, color = ID,
                              text = paste("Analyte: ", analyte,
                                           "<br> Ratio: ", od_ratio,
                                           "<br> Class: ", category))) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
  # guides(size = "none") +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
        legend.position = c(0.1,0.78)) +
  xlab("Analytes") +
  ylab("Indoor to Outdoor Ratios") +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment: Mmm. dd - Mmm. dd, YYYY. City, CO")
ratio_plot + theme(
  legend.background = element_rect(fill = "#DADBDD"),
  legend.key = element_rect(fill = NA, color = NA)) 


```


```{r , fig.dim=c(13,10), warning=FALSE, message=FALSE}
ratio_plotly <- ggplot(indoor2, aes(x = reorder(analyte, od_ratio),
                              y = od_ratio, color = ID,
                              text = paste("Analyte: ", analyte,
                                           "<br> Ratio: ", od_ratio,
                                           "<br> Class: ", category))) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
  # guides(size = "none") +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
        legend.position = c(0.1,0.78)) +
  xlab("Analytes") +
  ylab("Indoor to Outdoor Ratios") +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment: Mmm. dd - Mmm. dd, YYYY. City, CO")
ggplotly(ratio_plotly, tooltip = "text")
```

```{r ratio_solar, out.width = "135%", warning=FALSE, message=FALSE}

solarized2 <- ggplot(indoor, aes(x = reorder(analyte, od_ratio),
                                y = od_ratio, color = ID,
                                text = paste("Analyte: ", analyte,
                                             "<br> Conc. :", conc.,
                                             "<br> Class: ", category))) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
  # guides(size = "none") +
  scale_y_log10(breaks = c(10e3, 10e2, 10e1, 10e0, 10e-1, 10e-2, 10e-3),
                labels = trans_format(`log10`, math_format(10^.x))) +
  theme_solarized() +
  scale_color_solarized() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  xlab("Analytes") +
  ylab("Indoor to Outdoor Ratios") +
  ggtitle("Site XXX: [NMAE] Summa Cannister Deployment")

solarized2 + theme(
  # Change legend background color
  legend.background = element_rect(fill = NA),
  legend.key = element_rect(fill = NA, color = NA))

```


```{r , fig.dim=c(13,10), warning=FALSE, message=FALSE}
ggplotly(solarized2, tooltip = "text")
```

---

## Different Themes

```{r pink_foam, out.width = "135%", warning=FALSE, message=FALSE }

pink_foam <- ggplot(voc, aes(x = reorder(analyte, conc.),
                           y = conc., color = ID)) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc.)) +
  # guides(size = "none") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  theme_gray() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  xlab("Analytes") +
  ylab("Concentration\n(VOC ppbv or methane ppmv)") +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")
pink_foam +
  scale_color_manual(values = c("#54bebe", "#006A4E",
                                "#e27c7c", "#503f3f", "#df979e",
                                "#c80064"),
                     labels = c("location1", "location2",
                                "location3", "Outdoor",
                                "location4", "location5")) +
  theme(legend.title = element_text(color = "black", size = 10),
        legend.text = element_text(color = "#261e1b"))

```


```{r yellow_rainbow, out.width = "135%", warning=FALSE, message=FALSE}

yellowrainbow <- ggplot(indoor, aes(x = reorder(analyte, od_ratio),
                                 y = od_ratio, color = ID)) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
  # guides(size = "none") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  xlab("Analytes") +
  ylab(expression(atop("Indoor to Outdoor Ratios"))) +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")

yellowrainbow + scale_color_manual(values = c("#EDDA74", "#ffc501",
                                              "#ff9801", "#037d50", "#024b30"),
                                   labels = c("location1", "location2",
                                              "location3", 
                                              "location4", "location5")) +
  theme(legend.title = element_text(color = "black", size = 10),
        legend.text = element_text(color = "#261e1b"))

```


```{r ice_cream, out.width = "135%", warning=FALSE, message=FALSE}

yellowrainbow + scale_color_manual(values = c("orchid", "chocolate4",
                                              "goldenrod2", "tomato2", "midnightblue"),
                                   labels = c("location1", "location2",
                                              "location3", 
                                              "location4", "location5")) +
  theme(legend.title = element_text(color = "black", size = 10),
        legend.text = element_text(color = "#261e1b"))


```


```{r viridis_magma, out.width = "135%", warning=FALSE, message=FALSE}

viridismagma <- ggplot(indoor, aes(x = reorder(analyte, od_ratio),
                                    y = od_ratio, color = ID)) +
  geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
  # guides(size = "none") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  dark_theme_gray() +
  scale_color_viridis(option = "plasma", discrete = TRUE) +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  xlab("Analytes") +
  ylab(expression(atop("Indoor to Outdoor Ratios"))) +
  ggtitle("Site XXX:[NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")
viridismagma


```


```{r economist_plot, out.width = "135%", warning=FALSE, message=FALSE}

eco <- ggplot(indoor, aes(x = reorder(analyte, od_ratio),
                      y = od_ratio, color = ID,
                              text = paste("Analyte: ", analyte,
                                           "<br> Ratio: ", od_ratio,
                                           "<br> Class: ", category))) +
              geom_point(shape = 18, size = 3, alpha = 0.5) +
  # geom_point(data = methane, aes(x = analyte, y = conc., size = 1.5)) +
  # guides(size = "none") +
  scale_y_log10(labels = trans_format(`log10`, math_format(10^.x))) +
  theme_economist() +
  scale_color_economist() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 0)) +
  xlab("Analytes") +
  ylab("Indoor to Outdoor Ratios") +
  ggtitle("Site XXX: [NAME] Summa Cannister Deployment",
          "Mmm. dd - Mmm. dd, YYYY. City, CO")

ggplotly(eco, tooltip = "text")


```


```{r viridis_discrete, out.width = "135%", warning=FALSE, message=FALSE}

yellowrainbow + scale_colour_viridis(discrete = TRUE,
                                   labels = c("location1", "location2",
                                              "location3", 
                                              "location4", "location5")) +
  theme(legend.title = element_text(color = "black", size = 10),
        legend.text = element_text(color = "#261e1b"))

```

---

## Correlations
```{r cor_data, include=FALSE, warning=FALSE, message=FALSE}

#correlations
cor(outdoor$conc., location1$conc., method = "spearman")
#create a new df for correlation
voc_cor <- site_XXX %>% 
  slice(-3)
#convert select rows to numeric
voc_cor[2:62] <- lapply(voc_cor[2:62], as.numeric)
#run the correlation
vcor <- cor(voc_cor[, unlist(lapply(voc_cor, is.numeric))], method = "spearman")

```


```{r cor_table, include=FALSE}

datatable(voc_cor) 

```

```{r cor_matrix_upper, out.width = "150%", warning=FALSE, message=FALSE}

#upper w/ diag lables
corrplot(vcor, method = "color", type = "upper", tl.col = "black",
         tl.srt = 45, tl.cex = 0.5)

```


```{r cor_matrix_lower, out.width = "150%", warning=FALSE, message=FALSE}

#upper w/ diag lables
corrplot(vcor, method = "color", type = "lower", tl.col = "black",
         col = viridis(12), tl.srt = 45, tl.cex = 0.5)

```

```{r cor_matrix, out.width = "150%", warning=FALSE, message=FALSE}

#upper w/ diag lables
corrplot(vcor, method = "color", tl.col = "black", tl.cex = 0.5)

```



